\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

\medskip 
Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media. A number of computational methods have been developed to accurately represent force balances in Darcean flows. Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success. However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}. Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.

>>>>

\medskip 
Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media. Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows. Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success. However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}. Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
